\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem,hyperref}
\usepackage{xcolor}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}

% Color settings for hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Mayank Sahu}} \\
    {\small Software Developer | Resume Optimization | AI Integration} \\
    \href{mailto:your.email@example.com}{your.email@example.com} | +91 XXXXXXXXXX | \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile} | \href{https://github.com/yourgithub}{github.com/yourgithub}
\end{center}

\hrule

\section*{Summary}
Software developer with experience in resume optimization, ATS integration, and AI-driven content generation. Passionate about creating efficient, scalable solutions that enhance career prospects and job application success.

\section*{Skills}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Programming: Python, JavaScript, LaTeX
    \item AI/ML: GPT-4o Integration, NLP, Resume Parsing
    \item Web Technologies: React.js, Node.js, REST APIs
    \item Tools: Git, Docker, AWS
\end{itemize}

\section*{Experience}
\textbf{Software Developer} \hfill Jan 2024 -- Present  \\
\textit{Freelance | Resume Optimization Project}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed an AI-powered resume generation tool integrating GPT-4o for job-specific customization.
    \item Processed LaTeX resume templates while ensuring ATS compatibility and formatting preservation.
    \item Designed an automation pipeline to match resumes with job descriptions for optimized applications.
\end{itemize}

\textbf{Full Stack Developer Intern} \hfill Jul 2023 -- Dec 2023  \\
\textit{XYZ Tech Solutions}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built and optimized web applications using React.js and Node.js.
    \item Developed APIs for seamless data communication between AI-based resume parsing services.
\end{itemize}

\section*{Projects}
\textbf{AI-Powered Resume Generator} 
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built a LaTeX-based resume processing system integrating GPT-4o to generate optimized resumes.
    \item Ensured formatting consistency while improving ATS suitability through NLP techniques.
\end{itemize}

\textbf{UAV-Based Disaster Identification System}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed an AI model for disaster detection using UAV data and real-time alerting mechanisms.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Technology (B.Tech), Computer Science} \hfill 2020 -- 2024 \\
XYZ University

\section*{Certifications}
\begin{itemize}[noitemsep,topsep=0pt]
    \item AWS Certified Cloud Practitioner
    \item Machine Learning with Python - Coursera
\end{itemize}

\section*{Languages}
English (Fluent), Hindi (Native), Punjabi (Conversational)

\hrule

\end{document}